### 2019-03-26 jpdc/tex/optimization.tex
Add jpdc.

\begin{figure}
    \centering
    \begin{minipage}{0.42\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{fig/reduce_cdf} % first figure itself
		\caption{Shuffle Time Fraction CDF of OpenCloud Trace}
		\label{fig:cdf}
    \end{minipage}\hfill
    \begin{minipage}{0.49\textwidth}
        \centering
        \includegraphics[width=\textwidth]{fig/sim} % second figure itself
		\caption{Stage Completion Time Improvement of OpenCloud Trace}
		\label{fig:sim}
    \end{minipage}
\end{figure}

% \begin{figure}
% 	\centering
% 	\includegraphics[width=0.45\linewidth]{fig/reduce_cdf}
% 	\caption{Shuffle Time Fraction CDF of OpenCloud Trace}
% 	\label{fig:cdf}
% 	\vspace{10em}
% \end{figure}

% \begin{figure}
% 	\centering
% 	\includegraphics[width=0.4\linewidth]{fig/sim}
% 	\caption{Stage Completion Time Improvement of OpenCloud Trace}
% 	\label{fig:sim}
% 	\vspace{-1em}
% \end{figure}

@@

From the perspective of reduce task, SCache provides an API named $getBlock$ to replace the original implementation of shuffle read. 
With the precondition of shuffle data pre-fetching, 
the $getBlock$ leverages the memory copy to fetch the shuffle data from the local memory of SCache.
% Instead, the original implementation of shuffle read will trigger an all-to-all network transfer that keeps CPU idle.
%To this end, all I/O operations are managed outside of the DAG framework, and the slot is occupied only by the CPU intensive phases of task.
\subsection{Pre-schedule with Application Context}
The pre-scheduling and pre-fetching are the most critical aspects of the optimization. 
The task-node mapping is not determined until tasks are scheduled by the scheduler of DAG framework. 
Once the tasks are scheduled, the slots will be occupied to launch them. 
On the other hand, the shuffle data cannot be pre-fetched without the awareness of task-node mapping.
We propose a co-scheduling scheme with two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}). 
That is, the task-node mapping is established a priori, and then it is enforced by the co-scheduler when the DAG framework starts task scheduling. 
% We explore several pre-scheduling schemes in different scenarios, and evaluate the performance calculating the improvement of reduce tasks completion time with trace of OpenCloud \cite{opencloudtrace}. We first emulate the scheduling algorithm of Spark to schedule the reduce tasks of one job, and take the bottleneck of the task set as the completion time. Then we remove the shuffle read time as the assumption of shuffle data pre-fetch and emulate under different schemes. The result is shown in \ref{fig:sim}.
% \begin{figure*}
% 	\centering
% 	\begin{minipage}{0.34\linewidth}
% 		\begin{figure}[H]
% 			\includegraphics[width=\textwidth]{fig/shuffle_size}
% 			\caption{Shuffle Size Comparing with Input Size}
% 			\label{fig:shuffle_size}
% 		\end{figure}
% 	\end{minipage}
% 	\begin{minipage}{0.65\linewidth}
% 		\begin{figure}[H]
% 			\begin{subfigure}{0.5\textwidth}
% 				\includegraphics[width=\linewidth]{fig/reduce_cdf}
% 				\caption{Shuffle Time Fraction CDF}
% 				\label{fig:cdf}
% 			\end{subfigure}	
% 			\begin{subfigure}{0.5\textwidth}
% 				\includegraphics[width=\linewidth]{fig/sim}
% 				\caption{Stage Completion Time Improvement}
% 				\label{fig:sim}
% 			\end{subfigure}	
% 			\caption{Emulate Result of OpenCloud Trace}
% 		\end{figure}
% 	\end{minipage}
% \end{figure*}
% \begin{figure}
\subsubsection{Problem of Random Mapping}\label{randomassign}
The simplest way of pre-scheduling is mapping tasks to nodes randomly and evenly. 
In order to evaluate the effectiveness of random mapping, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
Note that most of the traces from OpenCloud are shuffle-light workload as shown in Figure \ref{fig:cdf}. 
The average shuffle read time is $3.2\%$ of total reduce completion time.

\begin{figure}
	\centering
	\includegraphics[width=0.5\linewidth]{fig/shuffle}
	\caption{Shuffle Data Prediction}
	\label{fig:shuffle}
	\vspace{-1em}
\end{figure}
As shown in Figure \ref{fig:sim}, the baseline (i.e., red dotted line) is the stage completion time with Spark FIFO scheduling algorithm. 
We then remove the shuffle read time of each task and run the simulation under three scheduling schemes: random mapping, Spark FIFO, and our heuristic MinHeap.
Random mapping works well when there is only one round of tasks, but the performance drops as the round number grows. 
This is because that data skew commonly exists in data-parallel computing \cite{skewtune, reining, gufler2012load}. 
Several heavy tasks may be assigned to the same node, thus slowing down the whole stage. 
In addition, randomly assigned tasks also ignore the data locality between shuffle map output and reduce input, which may introduce extra network traffic in cluster.

@@

\begin{figure*}
	\centering
	\begin{subfigure}[b]{0.31\linewidth}
		\includegraphics[width=\linewidth]{fig/hash_pre}
		\caption{Linear Regression Prediction of Hash Partitioner\newline}
		\label{fig:hash_pre}
	\end{subfigure}
	\begin{subfigure}[b]{0.31\linewidth}
		\includegraphics[width=\linewidth]{fig/range_pre_sample}
		\caption{Linear Regression and Sampling Prediction of Range Partitioner}
		\label{fig:range_pre_sample}
	\end{subfigure}
	\begin{subfigure}[b]{0.31\linewidth}
		\includegraphics[width=\linewidth]{fig/prediction_relative_error}
		\caption{Prediction Relative Error of Range Partitioner\newline}
		\label{fig:prediction_relative_error}
	\end{subfigure}
	\caption{Reduction Distribution Prediction}
	\label{fig:dis}
	\vspace{-1em}
\end{figure*}

@@

% Several map outputs (marked as Map Output in Figure \ref{fig:shuffle}) are picked as observation objects to train the model and than predict the final reduce distribution.
% \ifrevision
% \reversemarginpar
% \marginpar{D6,E3}
% \fi
To handle this corner case, we introduce another methodology, named \emph{weighted reservoir sampling}, as a substitution of linear regression. 
Note that linear regression will be replaced only when a RangePartitioner or a customized non-hash partitioner occurs. 
For each map task, we use classic reservoir sampling to randomly pick $s \times p$ of samples, where $p$ is the number of reduce tasks and $s$ is a tunable number. 
After that, the map function is called locally to process the sampled data (\textit{Sampling} in Figure \ref{fig:shuffle}). 
Finally, the partitioned outputs are collected with the $InputSize_j$ as the weight of the samples.
Note that sampling does not consume the input data of map tasks. 
The $BlockSize_{ji}$ can be calculated by:
\begin{equation}
\label{equationsample}
\begin{aligned}
	BlockSize_{ji} &= {{InputSize_j \times \frac{sample_i}{s \times p}}} \\
	sample_i &= \text{number of samples for $reduce_i$}
\end{aligned}
\end{equation}
% The classic reservoir sampling is designed for randomly choosing \textit{k} samples from \textit{n} items, where \textit{n} is either a very large or an unknown number \cite{reservoir}. 
In Figure \ref{fig:range_pre_sample}, when $s$ is set to $3$, the result of sampling prediction is much better than linear regression. 
The variance of the normalization between sampling prediction and reduce distribution is because the standard deviation of the prediction results is relatively small compared to the average prediction size, which is $0.0015$ in this example. 
Figure \ref{fig:prediction_relative_error} further proves that the sampling prediction can provide precise result even in the dimension of absolute input size of reduce task. 
On the other hand, the result of linear regression comes out with a large relative error. 
Though the weighted reservoir sampling is precise, it also introduced extra overhead. 
We will show the overhead evaluation of sampling in Section \ref{evaluation}.

@@

\noindent
\begin{minipage}{0.95\columnwidth}
\begin{algorithm}[H]
\caption{Heuristic MinHeap Scheduling for Single Shuffle}
\label{hminheap}
	\begin{algorithmic}[1]
	\small
	\Procedure{schedule}{$m, host\_ids, p\_reduces$}
		\State $m\gets$ partition number of map tasks
		\State $R\gets$ sort $p\_reduces$ by size in non-increasing order
		\State $M\gets$ min-heap $\left\{ host\_id \rightarrow \left( \left[ reduces \right], size \right) \right\}$
		\State $idx\gets 0$
		\State\While{$idx <$ len$R$}
			% \Comment{Schedule reduces by MinHeap}
			\State $M\left[0\right].size \mathrel{+}= R\left[idx\right].size$
			\State $M\left[0\right].reduces.append\left(R\left[idx\right]\right)$
			\State $R\left[idx\right].assigned\_id \gets M \left[0\right].host\_id$
			\State Sift down $M\left[0\right]$ by $size$
			\State $idx\gets idx-1$
		\EndWhile
		\State $max\gets$ maximum size in $M$
		% \State Convert $M$ to mapping $\left\{ host\_id \rightarrow \left( \left[ rid\_arr \right], size \right) \right\}$
		\ForAll{$reduce$ in $R$}
		\Comment{Heuristic locality swap}
			\If{$reduce.assigned\_id \neq reduce.host\_id$}
				\State $p\gets reduce.prob$
				\State $norm\gets \left(p-1/m\right)/\left(1-1/m\right)/10$
				\State $upper\_bound \gets \left(1 + norm\right) \times max$
				\State SWAP\_TASKS$\left(M, reduce, upper\_bound\right)$
			\EndIf
		\EndFor
		% \Comment{$m$ is the number of input data}
		% \Comment{$r$ is partition number of reduces}
		% \Comment{$hosts$ is array of (hostid, partitionids[], size)}
		% \Comment{$c$ is $r*m$ array of composition data}
		% \Comment{$pSize$ is $r$ size array of predicted size of reduces}
		\Return $M$
	\EndProcedure
	\Procedure{swap\_tasks}{$M, reduce, upper\_bound$}
		\State Swap tasks between node $host\_id$ and node $assigned\_id$
		\State of $reduce$ without exceeding the $upper\_bound$
		\State of both nodes.
		\State Return if it is impossible.
		% \State $reduces \gets M\left[reduce.host\_id\right].reduce$	
		% \State $candidates \gets$ Select from $reduces$ that $assigned\_id \neq host\_id$ \textbf{and} total size closest to $reduce.size$
		% \State $\Delta size \gets sizeOf\left(candidates\right) - reduce.size$
		% \State $size\_host \gets M\left[reduce.host\_id\right].size - \Delta size$
		% \State $size\_assigned \gets M\left[reduce.assigned\_id\right].size + \Delta size$
		% \If{$size\_host\leq upper\_bound$ \textbf{and} \\
		% 	\qquad \; $size\_assigned\leq upper\_bound$}
		% 	\State Swap $candidates$ and $reduce$
		% 	\State Update $size$ in $M$
		% 	\State Update $assigned\_host$ in $candidates$ and $reduce$
		% \EndIf
	\EndProcedure
	\end{algorithmic}
\end{algorithm}
\end{minipage}

>>>>

\begin{figure}
    \centering
    % \begin{minipage}{0.42\textwidth}
    %     \centering
    %     \includegraphics[width=0.9\textwidth]{fig/reduce_cdf} % first figure itself
	% 	\caption{Shuffle Time Fraction CDF of OpenCloud Trace}
	% 	\label{fig:cdf}
    % \end{minipage}\hfill
    \begin{minipage}{0.42\textwidth}
        \centering
        \includegraphics[width=\textwidth]{fig/sim} % second figure itself
		\caption{Stage Completion Time Improvement of OpenCloud Trace}
		\label{fig:sim}
	\end{minipage}
	\begin{minipage}{0.49\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{fig/shuffle} % first figure itself
		\caption{Shuffle Data Prediction}
		\label{fig:shuffle}
    \end{minipage}\hfill
\end{figure}

@@

From the perspective of reduce task, SCache provides an API named $getBlock$ to replace the original implementation of shuffle read. 
With the precondition of shuffle data pre-fetching, 
the $getBlock$ leverages the memory copy to fetch the shuffle data from the local memory of SCache.
% Instead, the original implementation of shuffle read will trigger an all-to-all network transfer that keeps CPU idle.
%To this end, all I/O operations are managed outside of the DAG framework, and the slot is occupied only by the CPU intensive phases of task.
\subsection{Pre-schedule with Application Context}
The pre-scheduling and pre-fetching are the most critical aspects of the optimization. 
The task-node mapping is not determined until tasks are scheduled by the scheduler of DAG framework. 
Once the tasks are scheduled, the slots will be occupied to launch them. 
On the other hand, the shuffle data cannot be pre-fetched without the awareness of task-node mapping.
We propose a co-scheduling scheme with two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}). 
That is, the task-node mapping is established a priori, and then it is enforced by the co-scheduler when the DAG framework starts task scheduling. 
% We explore several pre-scheduling schemes in different scenarios, and evaluate the performance calculating the improvement of reduce tasks completion time with trace of OpenCloud \cite{opencloudtrace}. We first emulate the scheduling algorithm of Spark to schedule the reduce tasks of one job, and take the bottleneck of the task set as the completion time. Then we remove the shuffle read time as the assumption of shuffle data pre-fetch and emulate under different schemes. The result is shown in \ref{fig:sim}.
% \begin{figure*}
% 	\centering
% 	\begin{minipage}{0.34\linewidth}
% 		\begin{figure}[H]
% 			\includegraphics[width=\textwidth]{fig/shuffle_size}
% 			\caption{Shuffle Size Comparing with Input Size}
% 			\label{fig:shuffle_size}
% 		\end{figure}
% 	\end{minipage}
% 	\begin{minipage}{0.65\linewidth}
% 		\begin{figure}[H]
% 			\begin{subfigure}{0.5\textwidth}
% 				\includegraphics[width=\linewidth]{fig/reduce_cdf}
% 				\caption{Shuffle Time Fraction CDF}
% 				\label{fig:cdf}
% 			\end{subfigure}	
% 			\begin{subfigure}{0.5\textwidth}
% 				\includegraphics[width=\linewidth]{fig/sim}
% 				\caption{Stage Completion Time Improvement}
% 				\label{fig:sim}
% 			\end{subfigure}	
% 			\caption{Emulate Result of OpenCloud Trace}
% 		\end{figure}
% 	\end{minipage}
% \end{figure*}
% \begin{figure}
\subsubsection{Problem of Random Mapping}\label{randomassign}
The simplest way of pre-scheduling is mapping tasks to nodes randomly and evenly. 
In order to evaluate the effectiveness of random mapping, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
% Note that most of the traces from OpenCloud are shuffle-light workload as shown in Figure \ref{fig:cdf}. 
The average shuffle read time is $3.2\%$ of total reduce completion time.

As shown in Figure \ref{fig:sim}, the baseline (i.e., red dotted line) is the stage completion time with Spark FIFO scheduling algorithm. 
We then remove the shuffle read time of each task and run the simulation under three scheduling schemes: random mapping, Spark FIFO, and our heuristic MinHeap.
Random mapping works well when there is only one round of tasks, but the performance drops as the round number grows. 
This is because that data skew commonly exists in data-parallel computing \cite{skewtune, reining, gufler2012load}. 
Several heavy tasks may be assigned to the same node, thus slowing down the whole stage. 
In addition, randomly assigned tasks also ignore the data locality between shuffle map output and reduce input, which may introduce extra network traffic in cluster.

@@

\begin{figure*}
	\centering
	\begin{subfigure}[b]{0.31\linewidth}
		\includegraphics[width=\linewidth]{fig/hash_pre}
		\caption{Linear Regression Prediction of Hash Partitioner\newline}
		\label{fig:hash_pre}
	\end{subfigure}
	\begin{subfigure}[b]{0.31\linewidth}
		\includegraphics[width=\linewidth]{fig/range_pre_sample}
		\caption{Linear Regression and Sampling Prediction of Range Partitioner2222}
		\label{fig:range_pre_sample}
		\vspace{1em}
	\end{subfigure}
	\begin{subfigure}[b]{0.31\linewidth}
		\includegraphics[width=\linewidth]{fig/prediction_relative_error}
		\caption{Prediction Relative Error of Range Partitioner\newline}
		\label{fig:prediction_relative_error}
	\end{subfigure}
	\caption{Reduction Distribution Prediction}
	\label{fig:dis}
	\vspace{-1em}
\end{figure*}

@@

% Several map outputs (marked as Map Output in Figure \ref{fig:shuffle}) are picked as observation objects to train the model and than predict the final reduce distribution.
% \ifrevision
% \reversemarginpar
% \marginpar{D6,E3}
% \fi

\noindent
\begin{minipage}{0.95\columnwidth}
\begin{algorithm}[H]
\caption{Heuristic MinHeap Scheduling for Single Shuffle}
\label{hminheap}
	\begin{algorithmic}[1]
	\small
	\Procedure{schedule}{$m, host\_ids, p\_reduces$}
		\State $m\gets$ partition number of map tasks
		\State $R\gets$ sort $p\_reduces$ by size in non-increasing order
		\State $M\gets$ min-heap $\left\{ host\_id \rightarrow \left( \left[ reduces \right], size \right) \right\}$
		\State $idx\gets 0$
		\While{$idx <$ len$R$}
		% \Comment{Schedule reduces by MinHeap}
		\State $M\left[0\right].size \mathrel{+}= R\left[idx\right].size$
		\State $M\left[0\right].reduces.append\left(R\left[idx\right]\right)$
		\State $R\left[idx\right].assigned\_id \gets M \left[0\right].host\_id$
		\State Sift down $M\left[0\right]$ by $size$
		\State $idx\gets idx-1$
		\EndWhile
		\State $max\gets$ maximum size in $M$
		% \State Convert $M$ to mapping $\left\{ host\_id \rightarrow \left( \left[ rid\_arr \right], size \right) \right\}$
		\ForAll{$reduce$ in $R$}
		\Comment{Heuristic locality swap}
			\If{$reduce.assigned\_id \neq reduce.host\_id$}
				\State $p\gets reduce.prob$
				\State $norm\gets \left(p-1/m\right)/\left(1-1/m\right)/10$
				\State $upper\_bound \gets \left(1 + norm\right) \times max$
				\State SWAP\_TASKS$\left(M, reduce, upper\_bound\right)$
			\EndIf
		\EndFor
		\Return $M$
	\EndProcedure
	\Procedure{swap\_tasks}{$M, reduce, upper\_bound$}
		\State Swap tasks between node $host\_id$ and node $assigned\_id$
		\State of $reduce$ without exceeding the $upper\_bound$
		\State of both nodes.
		\State Return if it is impossible.
	\EndProcedure
	\end{algorithmic}
\end{algorithm}
\end{minipage}

To handle this corner case, we introduce another methodology, named \emph{weighted reservoir sampling}, as a substitution of linear regression. 
Note that linear regression will be replaced only when a RangePartitioner or a customized non-hash partitioner occurs. 
For each map task, we use classic reservoir sampling to randomly pick $s \times p$ of samples, where $p$ is the number of reduce tasks and $s$ is a tunable number. 
After that, the map function is called locally to process the sampled data (\textit{Sampling} in Figure \ref{fig:shuffle}). 
Finally, the partitioned outputs are collected with the $InputSize_j$ as the weight of the samples.
Note that sampling does not consume the input data of map tasks. 
The $BlockSize_{ji}$ can be calculated by:
\begin{equation}
\label{equationsample}
\begin{aligned}
	BlockSize_{ji} &= {{InputSize_j \times \frac{sample_i}{s \times p}}} \\
	sample_i &= \text{number of samples for $reduce_i$}
\end{aligned}
\end{equation}
% The classic reservoir sampling is designed for randomly choosing \textit{k} samples from \textit{n} items, where \textit{n} is either a very large or an unknown number \cite{reservoir}. 
% In Figure \ref{fig:range_pre_sample}, when $s$ is set to $3$, the result of sampling prediction is much better than linear regression. 
% The variance of the normalization between sampling prediction and reduce distribution is because the standard deviation of the prediction results is relatively small compared to the average prediction size, which is $0.0015$ in this example. 
% Figure \ref{fig:prediction_relative_error} further proves that the sampling prediction can provide precise result even in the dimension of absolute input size of reduce task. 
% On the other hand, the result of linear regression comes out with a large relative error. 
% Though the weighted reservoir sampling is precise, it also introduced extra overhead. 
% We will show the overhead evaluation of sampling in Section \ref{evaluation}.
{\color{blue}
Figure \ref{fig:prediction_relative_error} proves that the sampling prediction can provide much more accurate result than the linear regression. 
We will show the overhead evaluation of sampling in Section \ref{evaluation}. 
}

@@
